Calculation of gain coefficient in Dwayer relativistic discharge feedback model of thunderstorm runway breakdown

### 2018-09-30 AYSS-2018/article/main.tex
Правки от рецензента часть 2
abstract update

    \institute{Institute for Nuclear Research of RAS
        \and
        Moscow Institute of Physics and Technology (State University) 
        \and
        Space Research Institute of RAS
    }
    \abstract{%
        Some of modern models used to describe TGF phenomenon and lightning ignition suppose the existence of the positive positron or gamma ray feedback. The results of Monte-Carlo simulation presented in this work encourage to give a fresh look into this problem. Namely, the positive enhancement for experimentally observed electric fields in thunderclouds is not enough to produce positive feedback.
        %In modern models based on runway breakdown and created for explaining initiation of lighting and TGF phenomenon, there has been a strong emphasis on peak of positron annihilation in observed gamma-ray spectra. This observation used as evidence importance of positron feedback in thunderstorms. But in this report, we give some result of Monte-Carlo simulations speaking about weak influence of positrons on thunderstorm processes and appearance of TGF.
    }
    %
    \maketitle

@@

    Using simulation result we calculate gain coefficient by description from "Simulation" section. The result for the following cell parameters: primary electron energy~--- $3~MeV$, field area size~--- $400~meter$, electric field from $1$ to $2~kV/cm$, air density~--- $0.5~kg/m^3$ ($\sim 0.5~atm$) is presented at Fig.~\ref{pic-gain-a}. It can be clearly seen that the total gain factor is significantly smaller than one for fields less than $200~kV/m$. The gamma gain and positron gain are slight and don't exceed 6\%. Such small number could not explain self-sustaining discharge mechanism, proposed by Dwyer and gives only small contribution to the total charge generation.

>>>>

    \institute{Institute for Nuclear Research of RAS
        \and
        Moscow Institute of Physics and Technology (State University) 
        \and
        Space Research Institute of RAS
    }
    \abstract{%
        Some of modern models used to describe TGF phenomenon and lightning ignition suppose the existence of the positive positron or gamma ray feedback. In this article we present some results of Monte-Carlo simulation of development of electromagnetic avalanche in atmospheric conditions and calculation of gain coefficient for both positron and gamma-ray feedback. The calculations were maid both for realistic fields and acceleration cell sizes (up to 200 kV/m and 400 m respectively).
        The calculated gain coefficients for realistic fields and cell sizes are less than 10\% which strongly discourages use of positron and gamma feedback model to describe TGF phenomenon and other gamma-production mechanisms in atmosphere under normal conditions. The simulation also shows possibility of self-supporting positron feedback for extreme conditions like very high electric fields and very large cells.
    }
    %
    \maketitle

@@

    Using simulation result we calculate gain coefficient by description from "Simulation" section. The result for the following cell parameters: primary electron energy~--- $3~MeV$, field area size~--- $400~meter$, electric field from $1$ to $2~kV/cm$, air density~--- $0.5~kg/m^3$ ($\sim 0.5~atm$) is presented at Fig.~\ref{pic-gain-a}. It can be clearly seen that the total gain factor is significantly smaller than one for fields less than $200~kV/m$. The gamma gain and positron gain are slight and don't exceed 10\%. Such small number could not explain self-sustaining discharge mechanism, proposed by Dwyer and gives only small contribution to the total charge generation.
